---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(data.table)
library(ggplot2)
```

# Simulation study to phylogenetic decisiveness 

<!-- badges: start -->
<!-- badges: end -->

The goal of PhyloDecR_Simulation is to test random sets with n=6, 7, 8 taxa and compare speed and reply of Fischers Algorithm and the correct test (4-way partition property). 

**Definition** (4-way partition property). Let $S_n = \{Z_1, ..., Z_k\}$ be a set of quadruples of taxa set $X$, $\vert X \vert = n$. Then, $S_n$ satisfies the four-way partition property (for $X$) if, for all partitions of $X$ into four disjoint, nonempty sets $A_1, A_2, A_3$ and $A_4$ (with $A_1 \cup A_2 \cup A_3 \cup A_4 = X$) there exists $a_i \in A_i$ for $i = 1, 2, 3, 4$ for which $\{a_1, a_2, a_3, a_4\} \in S_n$.

**Theorem** (Theorem 2 of [M. Steel and M.J. Sanderson](https://www.sciencedirect.com/science/article/pii/S0893965909003000?via%3Dihub)). A collection $S_n$ of quadruples of $X$ is phylogenetically decisive if and only if $S_n$ satisfies the four-way partition property for $X$.

## Planned stuff

### Step 1: Create all partitions 

for n=6, 7, and 8 (these partitions are fix)

-> See scripts/CreatePartitionX.R 

The number of possible partitions is given by the Stirling numbers of the second kind: 

```{r}
source("helperFunctions/myStirlingFunction.R")
myStirlingFunction(n = 6,k=4)
myStirlingFunction(n = 7,k=4)
myStirlingFunction(n = 8,k=4)
myStirlingFunction(n = 9,k=4)
myStirlingFunction(n =10,k=4)

```


### Step 2: Create simulation function 

--> See helperFunctions/mySimulationFunction.R and mySimulationFunction_exact.R (the second one used only for n=6 as all possible combinations were below 10,000)

```{r}
# part of mySimulationFunction.R
# m = number of all possible quadruples for n taxa
# k = number of input quadruples

# Example 1: n=6, m=15, k=8, repeats=10000
n=6;m=15;k=8;repeats=10000
nr_allCombis = choose(m,k)
if(nr_allCombis<repeats) message("Testing all combination only once ...")
if(nr_allCombis<repeats) repeats = nr_allCombis 
message("Working on ",repeats," repeats of ", nr_allCombis," combinations")

# Example 2: n=7, m=35, k=18, repeats=10000
n=7;m=35;k=18;repeats=10000
nr_allCombis = choose(m,k)
if(nr_allCombis<repeats) message("Testing all combination only once ...")
if(nr_allCombis<repeats) repeats = nr_allCombis 
message("Working on ",repeats," repeats of ", nr_allCombis," combinations")

# Example 3: n=8, m=70, k=35, repeats=10000
n=8;m=70;k=35;repeats=10000
nr_allCombis = choose(m,k)
if(nr_allCombis<repeats) message("Testing all combination only once ...")
if(nr_allCombis<repeats) repeats = nr_allCombis 
message("Working on ",repeats," repeats of ", nr_allCombis," combinations")

```

### Step 3: Run simulations

--> See scripts/Simulation_nX.R

### Step 4: Summarize my results

--> See scripts/Simulation_Zusammenfassung.R

```{r}
load("results/SimulationResults_n6.RData")
load("results/SimulationResults_n7.RData")
load("results/SimulationResults_n8.RData")
source("helperFunctions/my4FTFunction.R")

SimulationResults_n6[,n:=6]
SimulationResults_n7[,n:=7]
SimulationResults_n8[,n:=8]

simData = rbind(SimulationResults_n6,
                SimulationResults_n7,
                SimulationResults_n8)
PlotData = data.table(n = rep(simData$n,2),
                      k = rep(simData$k,2),
                      phyloDec = c(simData$NR_FAlg_pos,simData$NR_PhyloDec),
                      category = c(rep("Algorithm",dim(simData)[1]),
                                   rep("4WPP",dim(simData)[1])))

ggplot(data=PlotData,aes(fill=category, y=phyloDec, x=k)) + 
  facet_wrap(vars(n),scales = "free_x") + 
  geom_bar(position="dodge", stat="identity")

stats_n6 = my4FTFunction(P = sum(SimulationResults_n6$NR_PhyloDec),
                         N = sum(SimulationResults_n6$NR_NotPhyloDec),
                         PP = sum(SimulationResults_n6$NR_FAlg_pos))
stats_n7 = my4FTFunction(P = sum(SimulationResults_n7$NR_PhyloDec),
                         N = sum(SimulationResults_n7$NR_NotPhyloDec),
                         PP = sum(SimulationResults_n7$NR_FAlg_pos))
stats_n8 = my4FTFunction(P = sum(SimulationResults_n8$NR_PhyloDec),
                         N = sum(SimulationResults_n8$NR_NotPhyloDec),
                         PP = sum(SimulationResults_n8$NR_FAlg_pos))
stats = rbind(stats_n6,stats_n7,stats_n8)
stats

```

# ToDo

* repeat stuff for n=9 and n=10?
* discuss with Mareike
