---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

<!-- badges: start -->

<!-- badges: end -->

I want to create a data table containing all possible four-way partitions with n=10 taxa. The data table should contain the following columns:

-   set_i: taxa included in partition i of 4, separated by "\|"
-   allQuads: all quadruples possible with the given partition, separated by "\|"

According to Stirling numbers of the second kind, there are 34,105 different partitions for 10 taxa.

There are nine types of partitions:

1)  a \| b \| c \| defghij
2)  a \| b \| cd \| efghij
3)  a \| b \| cde \| fghij
4)  a \| b \| cdef \| ghij
5)  a \| bc \| de \| fghij
6)  a \| bc \| def \| ghij
7)  a \| bcd \| efg \| hij
8)  ab \| cd \| ef \| ghij
9)  ab \| cd \| efg \| hij

I create them separately and combine them at the end.

In addition, I test the table with some example data sets (not decisive: Mareikes Mathematica example, decisive: some trees added to the previous example)

# Initialize

```{r}
rm(list = ls())
time0<-Sys.time()

source("../helperFunctions/myStirlingFunction.R")
source("../helperFunctions/myPartitioningFunction.R")

library(PhyloDecR)
library(data.table)
library(foreach)
```

# Check & general parameters

```{r}
myStirlingFunction(n=10,k=4)

n=10
x = c(1:n)

```

# Set 1

a \| b \| c \| defghij

```{r}
allTriples = t(combn(n,3))
allTriples<-data.table::as.data.table(allTriples)
names(allTriples) = c("set1","set2","set3")

dumTab = foreach(i = 1:dim(allTriples)[1])%do%{
  #i=1
  myRow = allTriples[i,]
  myX = c(myRow$set1,myRow$set2,myRow$set3)
  notmyX = x[!is.element(x,myX)]
  
  myQuads = myPartitioningFunction(y1 = myRow$set1,
                                   y2 = myRow$set2,
                                   y3 = myRow$set3,
                                   y4 = notmyX)
  myRow[,set4 := paste(notmyX, collapse = "|")]
  myRow[,allQuads := myQuads]
  myRow
  
}

tab1 = rbindlist(dumTab)
head(tab1)
table(duplicated(tab1$allQuads))

```

# Set 2

a \| b \| cd \| efghij

```{r}
allTuples = t(combn(n,2))
allTuples<-data.table::as.data.table(allTuples)
names(allTuples) = c("set1","set2")

dumTab = foreach(i = 1:dim(allTuples)[1])%do%{
  #i=1
  myRow = allTuples[i,]
  myX = c(myRow$set1,myRow$set2)
  notmyX = x[!is.element(x,myX)]
  
  a = t(combn(length(notmyX),2))
  a1 = dim(a)[1]

  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set3:=paste(x2, collapse = "|")]
    myRow2[,set4:=paste(x3,collapse = "|")]
    
    myQuads = myPartitioningFunction(y1 = myRow2$set1,
                                     y2 = myRow2$set2,
                                     y3 = x2,
                                     y4 = x3)
    
    myRow2[,allQuads := myQuads]
    myRow2
  }
  
  myRow2 = rbindlist(dumTab2)
  myRow2
}

tab2 = rbindlist(dumTab)
head(tab2)
table(duplicated(tab2$allQuads))

```

# Set 3

a \| b \| cde \| fghij

```{r}
allTuples = t(combn(n,2))
allTuples<-data.table::as.data.table(allTuples)
names(allTuples) = c("set1","set2")

dumTab = foreach(i = 1:dim(allTuples)[1])%do%{
  #i=1
  myRow = allTuples[i,]
  myX = c(myRow$set1,myRow$set2)
  notmyX = x[!is.element(x,myX)]
  
  a = t(combn(length(notmyX),3))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set3:=paste(x2, collapse = "|")]
    myRow2[,set4:=paste(x3,collapse = "|")]
    
    myQuads = myPartitioningFunction(y1 = myRow2$set1,
                                     y2 = myRow2$set2,
                                     y3 = x2,
                                     y4 = x3)
    
    myRow2[,allQuads := myQuads]
    myRow2
  }
  
  myRow2 = rbindlist(dumTab2)
  myRow2
}

tab3 = rbindlist(dumTab)
head(tab3)
table(duplicated(tab3$allQuads))
tab3 = tab3[!duplicated(allQuads)]

```

# Set 4

a \| b \| cdef \| ghij

```{r}
allTuples = t(combn(n,2))
allTuples<-data.table::as.data.table(allTuples)
names(allTuples) = c("set1","set2")

dumTab = foreach(i = 1:dim(allTuples)[1])%do%{
  #i=1
  myRow = allTuples[i,]
  myX = c(myRow$set1,myRow$set2)
  notmyX = x[!is.element(x,myX)]
  
  a = t(combn(length(notmyX),4))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set3:=paste(x2, collapse = "|")]
    myRow2[,set4:=paste(x3,collapse = "|")]
    
    myQuads = myPartitioningFunction(y1 = myRow2$set1,
                                     y2 = myRow2$set2,
                                     y3 = x2,
                                     y4 = x3)
    
    myRow2[,allQuads := myQuads]
    myRow2
  }
  
  myRow2 = rbindlist(dumTab2)
  myRow2
}

tab4 = rbindlist(dumTab)
head(tab4)
table(duplicated(tab4$allQuads))
tab4 = tab4[!duplicated(allQuads)]

```

# Set 5

a \| bc \| de \| fghij

```{r}
allSingles = data.table(set1 = x)

dumTab = foreach(i = 1:dim(allSingles)[1])%do%{
  #i=8
  myRow = allSingles[i,]
  myX = c(myRow$set1)
  notmyX = x[!is.element(x,myX)]
  
  a = t(combn(length(notmyX),2))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=14
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set2:=paste(x2, collapse = "|")]
    
    b = t(combn(length(x3),2))
    b1 = dim(b)[1]
    
    dumTab3 = foreach(k = 1:b1)%do%{
      #k=7
      b2 = b[k,]
      myRow3 = copy(myRow2)
      
      x4 = x3[b2]
      x6 = x3[!is.element(x3,x4)]
      myRow3[,set3:=paste(x4, collapse = "|")]
      myRow3[,set4:=paste(x6, collapse = "|")]
      
      myQuads = myPartitioningFunction(y1 = myRow3$set1,
                                       y2 = x2,
                                       y3 = x4,
                                       y4 = x6)
      
      myRow3[,allQuads := myQuads]
      myRow3
    }
    dumTab3 = rbindlist(dumTab3)
    dumTab3
  }
  dumTab2 = rbindlist(dumTab2)
  dumTab2 = dumTab2[!duplicated(allQuads),]
  dumTab2
}

tab5 = rbindlist(dumTab)
head(tab5)
table(duplicated(tab5$allQuads))

```

# Set 6

a \| bc \| def \| ghij

```{r}
allSingles = data.table(set1 = x)

dumTab = foreach(i = 1:dim(allSingles)[1])%do%{
  #i=1
  myRow = allSingles[i,]
  myX = c(myRow$set1)
  notmyX = x[!is.element(x,myX)]
  
  a = t(combn(length(notmyX),2))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set2:=paste(x2, collapse = "|")]
    
    b = t(combn(length(x3),3))
    b1 = dim(b)[1]
    
    dumTab3 = foreach(k = 1:b1)%do%{
      #k=1
      b2 = b[k,]
      myRow3 = copy(myRow2)
      
      x4 = x3[b2]
      x6 = x3[!is.element(x3,x4)]
      myRow3[,set3:=paste(x4, collapse = "|")]
      myRow3[,set4:=paste(x6, collapse = "|")]
      
      myQuads = myPartitioningFunction(y1 = myRow3$set1,
                                       y2 = x2,
                                       y3 = x4,
                                       y4 = x6)
      
      myRow3[,allQuads := myQuads]
      myRow3
    }
    dumTab3 = rbindlist(dumTab3)
    dumTab3
  }
  dumTab2 = rbindlist(dumTab2)
  dumTab2 = dumTab2[!duplicated(allQuads),]
  dumTab2
}

tab6 = rbindlist(dumTab)
head(tab6)
table(duplicated(tab6$allQuads))

```

# Set 7

a \| bcd \| efg \| hij

```{r}
allSingles = data.table(set1 = x)

dumTab = foreach(i = 1:dim(allSingles)[1])%do%{
  #i=1
  myRow = allSingles[i,]
  myX = c(myRow$set1)
  notmyX = x[!is.element(x,myX)]
  
  a = t(combn(length(notmyX),3))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set2:=paste(x2, collapse = "|")]
    
    b = t(combn(length(x3),3))
    b1 = dim(b)[1]
    
    dumTab3 = foreach(k = 1:b1)%do%{
      #k=1
      b2 = b[k,]
      myRow3 = copy(myRow2)
      
      x4 = x3[b2]
      x6 = x3[!is.element(x3,x4)]
      myRow3[,set3:=paste(x4, collapse = "|")]
      myRow3[,set4:=paste(x6, collapse = "|")]
      
      myQuads = myPartitioningFunction(y1 = myRow3$set1,
                                       y2 = x2,
                                       y3 = x4,
                                       y4 = x6)
      
      myRow3[,allQuads := myQuads]
      myRow3
    }
    dumTab3 = rbindlist(dumTab3)
    dumTab3
  }
  dumTab2 = rbindlist(dumTab2)
  dumTab2 = dumTab2[!duplicated(allQuads),]
  dumTab2
}

tab7 = rbindlist(dumTab)
head(tab7)
table(duplicated(tab7$allQuads))


```

# Set 8

ab \| cd \| ef \| ghij

```{r}
allTuples = t(combn(n,2))
allTuples<-data.table::as.data.table(allTuples)
names(allTuples) = c("set1","set2")
allTuples[,tuple := paste(set1,set2,sep = "_")]
allTuples[,set2 := NULL]
allTuples[,set1 := NULL]

dumTab = foreach(i = 1:dim(allTuples)[1])%do%{
  #i=1
  myRow = allTuples[i,]
  myX = as.numeric(unlist(strsplit(myRow$tuple,"_")))
  notmyX = x[!is.element(x,myX)]
  myRow[,set1:=paste(myX, collapse = "|")]
  
  a = t(combn(length(notmyX),2))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set2:=paste(x2, collapse = "|")]
    
    b = t(combn(length(x3),2))
    b1 = dim(b)[1]
    
    dumTab3 = foreach(k = 1:b1)%do%{
      #k=1
      b2 = b[k,]
      myRow3 = copy(myRow2)
      
      x4 = x3[b2]
      x6 = x3[!is.element(x3,x4)]
      myRow3[,set3:=paste(x4, collapse = "|")]
      myRow3[,set4:=paste(x6, collapse = "|")]
      
      myQuads = myPartitioningFunction(y1 = myX,
                                       y2 = x2,
                                       y3 = x4,
                                       y4 = x6)
      
      myRow3[,allQuads := myQuads]
      myRow3[,tuple:=NULL]
      myRow3
    }
    dumTab3 = rbindlist(dumTab3)
    dumTab3
  }
  dumTab2 = rbindlist(dumTab2)
  dumTab2 = dumTab2[!duplicated(allQuads),]
  dumTab2
}
tab8 = rbindlist(dumTab)
head(tab8)
table(duplicated(tab8$allQuads))
tab8 = tab8[!duplicated(allQuads),]

```

# Set 9

ab \| bc \| efg \| hij

```{r}
allTuples = t(combn(n,2))
allTuples<-data.table::as.data.table(allTuples)
names(allTuples) = c("set1","set2")
allTuples[,tuple := paste(set1,set2,sep = "_")]
allTuples[,set2 := NULL]
allTuples[,set1 := NULL]

dumTab = foreach(i = 1:dim(allTuples)[1])%do%{
  #i=1
  myRow = allTuples[i,]
  myX = as.numeric(unlist(strsplit(myRow$tuple,"_")))
  notmyX = x[!is.element(x,myX)]
  myRow[,set1:=paste(myX, collapse = "|")]
  
  a = t(combn(length(notmyX),2))
  a1 = dim(a)[1]
  
  dumTab2 = foreach(j = 1:a1)%do%{
    #j=1
    a2 = a[j,]
    myRow2 = copy(myRow)
    
    x2 = notmyX[a2]
    x3 = notmyX[!is.element(notmyX,x2)]
    myRow2[,set2:=paste(x2, collapse = "|")]
    
    b = t(combn(length(x3),3))
    b1 = dim(b)[1]
    
    dumTab3 = foreach(k = 1:b1)%do%{
      #k=1
      b2 = b[k,]
      myRow3 = copy(myRow2)
      
      x4 = x3[b2]
      x6 = x3[!is.element(x3,x4)]
      myRow3[,set3:=paste(x4, collapse = "|")]
      myRow3[,set4:=paste(x6, collapse = "|")]
      
      myQuads = myPartitioningFunction(y1 = myX,
                                       y2 = x2,
                                       y3 = x4,
                                       y4 = x6)
      
      myRow3[,allQuads := myQuads]
      myRow3[,tuple:=NULL]
      myRow3
    }
    dumTab3 = rbindlist(dumTab3)
    dumTab3
  }
  dumTab2 = rbindlist(dumTab2)
  dumTab2 = dumTab2[!duplicated(allQuads),]
  dumTab2
}
tab9 = rbindlist(dumTab)
head(tab9)
table(duplicated(tab9$allQuads))
tab9 = tab9[!duplicated(allQuads),]


```

# Save

```{r}
myTab_n10 = rbind(tab1,tab2,tab3,tab4,tab5,tab6,tab7,tab8,tab9)
dim(myTab_n10)
myStirlingFunction(n=10,k=4)

stopifnot(dim(myTab_n10)[1]==myStirlingFunction(n=10,k=4))

myTab_n10[,status := "uncovered"]
myTab_n10[,count := 0]

save(myTab_n10,file = "../partitions/partitions_n10.RData")

```

# Test

```{r}
test1 = createInput(fn="../testData/S10_notDecisive.txt",sepSym = "_")
test1_checks = initialCheck(test1$data)
test1_alg<-runAlgorithm(data = test1$data,verbose = T)
test2 = createInput(fn="../testData/S10_Decisive.txt",sepSym = "_")
test2_checks = initialCheck(test2$data)
test2_alg<-runAlgorithm(data = test2$data,verbose = T)

dummy1 = test1$data
dummy2 = test2$data

dummy1 = dummy1[status=="input",]
dummy2 = dummy2[status=="input",]

myTab1 = copy(myTab_n10)
myTab2 = copy(myTab_n10)

for(i in 1:dim(dummy1)[1]){
  #i=1
  myInput = dummy1[i,quadruple]
  filt = grepl(myInput,myTab1$allQuads)
  myTab1[filt==T,status := "covered"]
  myTab1[filt==T,count := count + 1]
  myTab1
}
for(i in 1:dim(dummy2)[1]){
  #i=1
  myInput = dummy2[i,quadruple]
  filt = grepl(myInput,myTab2$allQuads)
  myTab2[filt==T,status := "covered"]
  myTab2[filt==T,count := count + 1]
  myTab2
}

table(myTab1$count)
table(myTab2$count)

if(min(myTab1$count>0)) message("phylogenetically decisive according to 4WPP") else message("not phylogenetically decisive")
if(min(myTab2$count>0)) message("phylogenetically decisive according to 4WPP") else message("not phylogenetically decisive")

```

# Session Info

```{r}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "mins"),3)," minutes")

```
