---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

<!-- badges: start -->

<!-- badges: end -->

I want to create a data table containing all possible four-way partitions with n=6 taxa. The data table should contain the following columns:

-   set_i: taxa included in partition i of 4, separated by "\|"
-   allQuads: all quadruples possible with the given partition, separated by "\|"

According to Stirling numbers of the second kind, there are 65 different partitions for 6 taxa.

There are two types of partitions:

1)  a \| b \| c \| def
2)  a \| b \| cd \| ef

I create them separately and combine them at the end.

In addition, I test the table with the example data set from my master thesis.

# Initialize

```{r}
rm(list = ls())
time0<-Sys.time()

source("../helperFunctions/myStirlingFunction.R")
source("../helperFunctions/myPartitioningFunction.R")
source("../helperFunctions/getAllPosQuads.R")

library(PhyloDecR)
library(data.table)
library(foreach)
```

# Check & general parameters

```{r}
myStirlingFunction(n=6,k=4)

myPartitioningFunction
getAllPosQuads

```

# Set 1

a \| b \| c \| def == 1 + 1 + 1 + 3

```{r}
tab1 = myPartitioningFunction(1,1,1,3)
```

# Set 2

a \| b \| cd \| ef == 1 + 1 + 2 + 2

```{r}
tab2 = myPartitioningFunction(1,1,2,2)

```

# Save

```{r}
myTab_n6 = rbind(tab1,tab2)
dim(myTab_n6)
myStirlingFunction(n=6,k=4)

stopifnot(dim(myTab_n6)[1]==myStirlingFunction(n=6,k=4))

myTab_n6[,status := "uncovered"]
myTab_n6[,count := 0]

save(myTab_n6,file = "../partitions/partitions_n6.RData")

```

# Test

```{r}
test1 = createInput(fn="../testData/S6_notDecisive.txt",sepSym = "_")
test1_checks = initialCheck(test1$data)
test1_alg<-runAlgorithm(data = test1$data,verbose = T)
test2 = createInput(fn="../testData/S6_Decisive.txt",sepSym = "_")
test2_checks = initialCheck(test2$data)
test2_alg<-runAlgorithm(data = test2$data,verbose = T)

dummy1 = test1$data
dummy2 = test2$data

dummy1 = dummy1[status=="input",]
dummy2 = dummy2[status=="input",]

myTab1 = copy(myTab_n6)
myTab2 = copy(myTab_n6)

for(i in 1:dim(dummy1)[1]){
  #i=1
  myInput = dummy1[i,quadruple]
  filt = grepl(myInput,myTab1$allQuads)
  myTab1[filt==T,status := "covered"]
  myTab1[filt==T,count := count + 1]
  myTab1
}
for(i in 1:dim(dummy2)[1]){
  #i=1
  myInput = dummy2[i,quadruple]
  filt = grepl(myInput,myTab2$allQuads)
  myTab2[filt==T,status := "covered"]
  myTab2[filt==T,count := count + 1]
  myTab2
}

table(myTab1$count)
table(myTab2$count)

if(min(myTab1$count>0)) message("phylogenetically decisive according to 4WPP") else message("not phylogenetically decisive")
if(min(myTab2$count>0)) message("phylogenetically decisive according to 4WPP") else message("not phylogenetically decisive")

```

# Session Info

```{r}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "mins"),3)," minutes")

```
