---
output: github_document
---

<!-- Simulation_n9.md is generated from Simulation_n9.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

<!-- badges: start -->

<!-- badges: end -->

I want to run a simulation for n=9 taxa. There are 126 possible quadruples with n=9 taxa, and I want to test all possible combinations for k out of 126 quadruples for phylogenetic decisiveness.

For each random set of quadruples, I test both the 4-way-partition-property (**4WPP**, truth) and Fischers algorithm (**FAlg**, test). 

# Initialize

I use a file names *mySourceFile.R* that contains all relevant R packages and user-/server-specific path to the R library. If using this code, you must make all the necessary changes within the template source file. 

```{r init}
rm(list = ls())
time0<-Sys.time()

source("../mySourceFile.R")
source("../helperFunctions/mySimulationFunction.R")

```

# Get input data

In *myTab_n9*, there are all possible Four-way-partitions (4WP) given n=9 taxa. 

In *quadruple_data*, there are all possible quadruples given n=9 taxa. 

```{r input}
test1 = createInput(fn="../testData/S9_Decisive.txt",sepSym = "_")
quadruple_data = test1$data
quadruple_data[,status:=NA]
max_quad = dim(quadruple_data)[1]-1

load("../partitions/partitions_n9.RData")
```

# Test loop with 100 repeats

To test my simulation loop, I run it with only 100 repeats (should be rather fast).

```{r test}
time3 = Sys.time()
dumTab2 = foreach(j=1:max_quad)%do%{
  # j=10
  message("\nWorking on n=9, k=",j," & rep = 100 ... ")
  time1 = Sys.time()
  myTest = mySimulationFunction(number_taxa = 9, 
                                number_quads = j,
                                repeats = 100,
                                data1 = quadruple_data,
                                data2 = myTab_n9,
                                verbose = F)
  time2 = Sys.time()
  x0 = as.numeric(round(difftime(time2,time1,units = "mins"),3))
  message("       Total time for n=9, k=",j," & rep = 100: " ,round(difftime(time2,time1,units = "mins"),3)," minutes")
  
  x1 = myTest$check3 == "CHECK 3 NOT OK - NOT PHYLOGENETICALLY DECISIVE" & 
    myTest$FWPP == "NOT PHYLOGENETICALLY DECISIVE"
  x1 = sum(x1)
  x2 = myTest$FischersAlg == "PHYLOGENETICALLY DECISIVE" & 
    myTest$FWPP == "PHYLOGENETICALLY DECISIVE"
  x2 = sum(x2)
  x3 = myTest$FWPP == "NOT PHYLOGENETICALLY DECISIVE"
  x3 = sum(x3)
  x4 = myTest$FWPP == "PHYLOGENETICALLY DECISIVE"
  x4 = sum(x4)
  
  message("       There were ",x1," of ",x3," sets identified by my initial check as not decisive (",round(x1/x3,4)*100,"%)")
  message("       There were ",x2," of ",x4," sets identified by Fischers algorith as decisive (",round(x2/x4,4)*100,"%)")
  
  res = data.table(k = j,
                   time = x0,
                   NR_check3_neg = x1,
                   NR_FAlg_pos = x2,
                   NR_NotPhyloDec = x3,
                   NR_PhyloDec = x4)
  res
}
dumTab2 = rbindlist(dumTab2)
message("\nTIME for test loop: " ,round(difftime(Sys.time(),time3,units = "hours"),3)," hours")

dumTab2[,negRate := NR_check3_neg/NR_NotPhyloDec]
dumTab2[,posRate := NR_FAlg_pos/NR_PhyloDec]
dumTab2[NR_PhyloDec==0,posRate := NA]
dumTab2[NR_NotPhyloDec==0,negRate := NA]
dumTab2[NR_PhyloDec>0,]

```

# Loop with 10,000 repeats 


```{r simulation, eval=TRUE}
time4 = Sys.time()

registerDoMC(cores=10)

dumTab3 = foreach(j=1:max_quad)%dopar%{
  # j=10
  message("\nWorking on n=9, k=",j," & rep = max 10,000 ... ")
  time1 = Sys.time()
  myTest = mySimulationFunction(number_taxa = 9, 
                                number_quads = j,
                                repeats = 10000,
                                data1 = quadruple_data,
                                data2 = myTab_n9,
                                verbose = F)
  
  time2 = Sys.time()
  x0 = as.numeric(round(difftime(time2,time1,units = "mins"),3))
  message("       Total time for n=9, k=",j," & rep = 100: " ,round(difftime(time2,time1,units = "mins"),3)," minutes")
  
  outfn = paste0("../results/SimulationResults_n9_k",j,"_rep10000.RData")
  save(myTest,file = outfn)
  
  x1 = myTest$check3 == "CHECK 3 NOT OK - NOT PHYLOGENETICALLY DECISIVE" & 
    myTest$FWPP == "NOT PHYLOGENETICALLY DECISIVE"
  x1 = sum(x1)
  x2 = myTest$FischersAlg == "PHYLOGENETICALLY DECISIVE" & 
    myTest$FWPP == "PHYLOGENETICALLY DECISIVE"
  x2 = sum(x2)
  x3 = myTest$FWPP == "NOT PHYLOGENETICALLY DECISIVE"
  x3 = sum(x3)
  x4 = myTest$FWPP == "PHYLOGENETICALLY DECISIVE"
  x4 = sum(x4)
  
  message("       There were ",x1," of ",x3," sets identified by my initial check as not decisive (",round(x1/x3,4)*100,"%)")
  message("       There were ",x2," of ",x4," sets identified by Fischers algorith as decisive (",round(x2/x4,4)*100,"%)")
  
  res = data.table(k = j,
                   time = x0,
                   NR_check3_neg = x1,
                   NR_FAlg_pos = x2,
                   NR_NotPhyloDec = x3,
                   NR_PhyloDec = x4)
  res
}
SimulationResults_n9 = rbindlist(dumTab3)
message("\nTIME for simulation loop: " ,round(difftime(Sys.time(),time4,units = "hours"),3)," hours")

SimulationResults_n9[,negRate := NR_check3_neg/NR_NotPhyloDec]
SimulationResults_n9[,posRate := NR_FAlg_pos/NR_PhyloDec]
SimulationResults_n9[NR_PhyloDec==0,posRate := NA]
SimulationResults_n9[NR_NotPhyloDec==0,negRate := NA]
save(SimulationResults_n9, file = "../results/SimulationResults_n9.RData")

SimulationResults_n9[NR_PhyloDec>0,]

```

# Session Info

```{r sessionInfo}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "hours"),3)," hours")

```
