---
output: github_document
---

<!-- Simulation_n9.md is generated from Simulation_n9.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Summary of Simulations

<!-- badges: start -->

<!-- badges: end -->

What did I simulate?

**Preparation**: create all possible quadruples and all possible 4-way partitions (4WP) for $n=6, ..., 10$ taxa

**Simulation**: for $n$ taxa, there are $K_n=\binom{n}{4}$ possible quadruples. For each $k \in \{1, ..., K_n\}$, there are $M_k=\binom{K_n}{k}$ combinations of quadruples as input and 10,000 of these $M_k$ combinations are used in the simulation. Each combination is tested for phylogenetic decisiveness according to 4WP (truth) and Fischers algorithm (test). 

All simulation results are saved locally, the summary per $n$ is also stored on github.  

**Here**: Summary of the simulation results (barplots, negative predictive value, power). 
 
Upper border: it was already shown that given an input of $\binom{n}{4} - (n-4)$ quadruples, all sets are phylogenetic decisive: 
 
* $n=6$: $15-2 = 13$
* $n=7$: $35-3 = 32$
* $n=8$: $70-4 = 66$
* $n=9$: $126-5 = 121$
* $n=10$: $X-6 = Y$

Lower border: there is no simple formular, but I use here my lower bound from my master thesis (set size that covers all triples at least once):
 
* $n=6$: 6
* $n=7$: 11
* $n=8$: 14
* $n=9$: U
* $n=10$: V
 
# Initialize

I use a file names *mySourceFile.R* that contains all relevant R packages and user-/server-specific path to the R library. If using this code, you must make all the necessary changes within the template source file. 

```{r init}
rm(list = ls())
time0<-Sys.time()

source("../mySourceFile.R")
source("../helperFunctions/my4FTFunction.R")

x06_lb = 6
x06_ub = 13
x07_lb = 11
x07_ub = 32
x08_lb = 14
x08_ub = 66
x09_lb = 24
x09_ub = 121
#x10_lb = 14
#x10_ub = 66

```

# Get data

```{r input}
load("../results/SimulationResults_n6.RData")
load("../results/SimulationResults_n7.RData")
load("../results/SimulationResults_n8.RData")
load("../results/SimulationResults_n9.RData")

SimulationResults_n6[,n := 6]
SimulationResults_n7[,n := 7]
SimulationResults_n8[,n := 8]
SimulationResults_n9[,n := 9]

sim_n6 = SimulationResults_n6[k>=x06_lb & k<=x06_ub]
sim_n7 = SimulationResults_n7[k>=x07_lb & k<=x07_ub]
sim_n8 = SimulationResults_n8[k>=x08_lb & k<=x08_ub]
sim_n9 = SimulationResults_n9[k>=x09_lb & k<=x09_ub]

sim = rbind(sim_n6,sim_n7,sim_n8,sim_n9)
sim2 = rbind(SimulationResults_n6,SimulationResults_n7,
             SimulationResults_n8,SimulationResults_n9)
```

# Bar plots

```{r barplots}
dumTab1 = foreach(i = 6:9)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  x1 = dim(mySim)[1]
  
  PlotData = data.table(n = i, 
                        k = rep(mySim$k,2),
                        phyloDec = c(mySim$NR_FAlg_pos,mySim$NR_PhyloDec),
                        category = c(rep("Algorithm",x1),rep("4WPP",x1)))
  ggplot(data=PlotData,aes(fill=category, y=phyloDec, x=k)) + 
    geom_bar(position="dodge", stat="identity")
  
  PlotData
}
BarPlotData = rbindlist(dumTab1)

ggplot(data=BarPlotData,aes(fill=category, y=phyloDec, x=k)) + 
  facet_wrap(vars(n), nrow = 2, scales = "free") +
  geom_bar(position="dodge", stat="identity")

```

#  Contingency tables (overall)

* Prevalence = actual positive (P) / all (N+P)
* PPV = Positive Predictive Value = true positives (TP) / predicted positives (PP) = conditional probability P(true state positive | prediction positive)
* NPV = Negative Predictive Value = true negatives (TN) / predicted negatives = conditional probability P(true state negative | prediction negative)
* TPR = True Positive Rate = sensitivity = power = TP / P
* TNR = True Negative Rate = specificity = TN / N
* see also [Wikipedia](https://en.wikipedia.org/wiki/Positive_and_negative_predictive_values)


```{r  contingencyTables1, eval=TRUE}
dumTab2 = foreach(i = 6:9)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  stats_1 = my4FTFunction(P = sum(mySim$NR_PhyloDec),
                          N = sum(mySim$NR_NotPhyloDec),
                          PP = sum(mySim$NR_FAlg_pos))
  mySim2 = copy(sim2)
  mySim2 = mySim2[n == i,]
  stats_2 = my4FTFunction(P = sum(mySim2$NR_PhyloDec),
                          N = sum(mySim2$NR_NotPhyloDec),
                          PP = sum(mySim2$NR_FAlg_pos))
  
  stats = rbind(stats_1,stats_2)
  stats[,n:=i]
  stats[,setting := c("filtered","all")]
  stats
}
myStats = rbindlist(dumTab2)
myStats[setting == "filtered"]
myStats[setting == "all"]

```

**Fazit 1**: NPV is about 98%, i.e. there is a 98% probability that a negative set is really not phylogenically decisive 
 
**Fazit 2**: The power of the algorithm (TPR) is also about 98%. 

#  Contingency tables (per k)

```{r contingencyTables2}
dumTab3 = foreach(i = 6:9)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  
  dumTab4 = foreach(k = 1:dim(mySim)[1])%do%{
    # k=1
    myRow = copy(mySim)
    myRow = myRow[k,]
    
    stats_k = my4FTFunction(P = myRow$NR_PhyloDec,
                            N = myRow$NR_NotPhyloDec,
                            PP = myRow$NR_FAlg_pos)
    stats_k[,n :=i]
    stats_k[,k := k]
    stats_k[,status := "filtered"]
    stats_k
  }
  myStats_k = rbindlist(dumTab4)
  myStats_k
}
myStats_k = rbindlist(dumTab3)

filt_TPR = !is.na(myStats_k$TPR)
filt_NPV = !is.na(myStats_k$NPV)

boxplot(myStats_k$TPR[filt_TPR] ~ myStats_k$n[filt_TPR],
        xlab = "number of taxa",
        ylab = "power")
boxplot(myStats_k$NPV[filt_NPV] ~ myStats_k$n[filt_NPV],
        xlab = "number of taxa",
        ylab = "NPV")

tab6 = myStats_k[n==6,summary(TPR)]
tab7 = myStats_k[n==7,summary(TPR)]
tab8 = myStats_k[n==8,summary(TPR)]
tab9 = myStats_k[n==9,summary(TPR)]
tab_TPR = rbind(tab6,tab7,tab8,tab9)

tab6 = myStats_k[n==6,summary(NPV)]
tab7 = myStats_k[n==7,summary(NPV)]
tab8 = myStats_k[n==8,summary(NPV)]
tab9 = myStats_k[n==9,summary(NPV)]
tab_NPV = rbind(tab6,tab7,tab8,tab9)

tabs = as.data.table(rbind(tab_NPV,tab_TPR))
tabs[,n:=rep(c(6:9),2)]
tabs[,Parameter:=c(rep("NPV",4),rep("TPR",4))]
tabs = tabs[,c(9,8,1:7)]
tabs

```

# Session Info

```{r sessionInfo}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "hours"),3)," hours")

```
